\documentclass[11pt]{article}
\title{\textbf{Heatherhouse Lore}}
\author{Riedler}
\date{2023.07.12}

\usepackage{geometry}
\geometry{
 a4paper,
 left=25mm,
 right=25mm,
 top=10mm,
 bottom=25mm
}

\begin{document}

\maketitle

\section*{Heatherhouse the first}

the Heatherhouse with the househorns on the roof, with the heatherfans, making the hornergy to power the heatherhouse

\section*{Heathermouse}

Well in this heatherhouse there lives a little heathermouse, with a little heatherstove, in a little kitch-horn baking a lovely apple pie. But why? Her littlest heatherpup is having their first hornthday today! A celebration for the whole of heatherhouse!

\section*{Fountain}

Far from the heatherhouse, on top of a mountain, there was a fountain. And near that fountain, there were the four heathermice, playing with dice. All went well, but then it fell, into the fountain.
Not a big problem, thought the mice, and attempted to get back their dice. The first little mouse jumped in, but couldn't swim. The second mouse came and felt much the same. The third mouse was a bit fearful, so she stayed outside.\\
Then mother mouse stepped into the water and got them all out. It wasn't that deep, just the kids very small. The dice were lost and the mice very wet, but thanks to their mom, no ill fate had been met.

\section*{Heatherhorse}

Today was a slow day for the heatherhorse. Well, every day was, really. But he didn't mind. He'd gotten quite old over the years, and as old people tended to do, he slowed down. Of course he still enjoyed a good trot through the village, but not without stopping to admire some pretty flowers or busy critters along the way. Back in his youth, he always rushed past the scenery, full of energy and brimming with determination to use it. \emph{"What a shame"}, he thought, \emph{"there are some beautiful birds I could have looked at back then."} All in all, he was enjoying his retirement.

\newpage
\section*{Riedler's Pond}

Not far away from heatherhouse,\\
there's riedler with his pond.\\
It's got some little fishies,\\
of which he's very fond.\\
\\
One day, he got a visitor,\\
who came from very far.\\
They asked what he had fishes for,\\
which he found quite bizarre.\\
\\
\emph{"They provide me joy\\
when they are around.\\
Such cute carp and coy,\\
and others that I found."}\\
\\
The guest was sold,\\
they went to look,\\
and truth be told,\\
who knows how long they took…

\section*{Regards, the writer}

Down in the heathercellar,\\
there was a storyteller.\\
Not one made of flesh and blood,\\
but mechnical, though quite good.\\
\\
\emph{"A computer"}, she calls it,\\
though I don't believe that.\\
It glows and it's got wit.\\
could math have a chat?\\
\\
Anyway, I found this device to be very nice.\\
\\
I'm writing this all from here in the cellar\\
to riedler, the fediverse feller,\\
who forwards to those who like to behold\\
my lyrical writings, or so I was told.

\newpage
\section*{The Oracles}

On the mountain, near the fountain, there live two oracles. One knows everything that might happen, though not what will happen. At best, she can tell you what isn't going to happen, everything else is a big maybe. The other knows everything that is happening right now, but she once hit her head badly, so she can't remember any of it. There used to be a third who could see the past, but nobody knows what happened to her, since that would be her job to do. The other two miss her greatly, though mostly for practical reasons.\\
\\
The heathermouse often visit them with her kids and brings cake and pastries. The first little mouse thinks she might become an oracle in the future. The second little mouse wants to be an oracle right now, but he's too shy to ask. The third little mouse insists that she was an oracle in her past life, but nobody believes her. She doesn't mind though, usually being occupied with telling stories that might have happened.

\end{document}
